---
title: "MLM - ex1"
author: "Tomer Zipori"
format: html
execute: 
  warning: false
  message: false
  cache: true
editor: visual
---

# Setup
```{r}
#| output: false
library(tidyverse)
library(performance)
library(parameters)
library(lmerTest)
library(sjPlot)
```

# Loading data
```{r}
dataset2 <- read.csv("Example- Couples relational Satisfaction.csv")

head (dataset2)
```

## Converting to long format
```{r}
data_long <- dataset2 |>
  pivot_longer(cols = c(M_sat, F_sat),
               names_to = "gender",
               values_to = "satisfaction") |>
  mutate(gender = case_when(gender == "M_sat" ~ "male",
                            gender == "F_sat" ~ "female"))
```

# Part I
## Empty model
```{r}
model_A <- lm(satisfaction ~ 1, data = data_long)

summary(model_A)
```
The intercept in the empty model is equal to the grand mean of the Dependent variable. In this case it is $1.1401$.

## Random intercepts model
```{r}
model_B <- lmer(satisfaction ~ 1 + (1 | ID), data = data_long)

parameters(model_B)
```
## How much variance is explained by the random intercepts?
```{r}
icc(model_B)
```
51.2% of the variance in the dependent variable is explained by the random intercepts of each couple.

### Model comparison
```{r}
ranova(model_B)
```

The addition of explained variance by the random intercepts is **significant**.
AIC measures also indicate that model1 is better fitted to the data (small AIC = better fit).


# Part 2
## Model C - predicting satisfaction from gender (no random effects)
```{r}
model_C <- lm(satisfaction ~ gender, data = data_long)

summary(model_C)
```

## Model D - predicting satisfaction from gender (with random intercepts and slopes per couple)
```{r}
model_D <- lmer(satisfaction ~ gender + (1 | ID), data = data_long)

parameters(model_D)
```

## Model E - adding duration and (with random intercepts)
```{r}
model_E <- lmer(satisfaction ~ Duration * gender + (1 | ID), data = data_long)

parameters(model_E)
```

## Model comparison
### Models C and D
```{r}
ranova(model_D)

bayestestR::bayesfactor_models(model_C, model_D)
```
Significant support for the model with random effects.

### Models D and E
```{r}
anova(model_D, model_E, refit = F)
```
Significant support for the model with `Duration` and `Duration X gender` interaction parameters.



